Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
reivew disc
Further fixes

\subsubsection{Continuing Change} %Reviewed by WJ
The case company described that including new functional content was one of the top priorities for the release of vesrion 2.0. This is supported by the characteristic of the changes identified in this study. 4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules. It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause. One of the main reasons for continuously adapting the API is also to control the way API users use the API. Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API. These applications were fully functional, but there existed no standard method of implementation. We therefore conclude that the law of continuing change holds for APIs.

@@

%API users should be included in the design process? 
\smallskip \noindent 
\textbf{Maintainability does not drive change  }  
While maintainability is important, it is not a primary driving factor for change. We found that where changes that effected maintainability, functionality had also been added or modified. Of the changes identified, none were considered to be primarily groomative. Groomative motives were only found to be secondary, and were never the main motive for a change. Changes to the example code are an instance of this. The example code was updated purely to reflect the changes in functionality and not as a groomative effort.

>>>>

\subsubsection{Continuing Change} %Reviewed by WJ
The case company described that including new functional content was one of the top priorities for the release of version 2.0. This is supported by the characteristic of the changes identified in this study. 4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules. It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause. One of the main reasons for continuously adapting the API is also to control the way API users use the API. Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API. These applications were fully functional, but there existed no standard method of implementation. We therefore conclude that the law of continuing change holds for APIs.

@@

\smallskip \noindent 
\textbf{Maintainability does not drive change  }  
While maintainability is important, it is not a primary driving factor for change. We found that where changes that effected maintainability, functionality had also been added or modified. Of the changes identified, none were considered to be primarily groomative. Groomative motives were only found to be secondary, and were never the main motive for a change. Changes to the example code are an instance of this. The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
